Data analytics effects in Baseball player's value

### 2023-12-16 manuscription/manuscription.tex
Improved introdcution section.
Improving method section, result section and discussion

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{url}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

在添加一些部分在这

\cite*{web:Wyers:Part2}

@@

\section{Data}
\label{sec:data}
Following are definitions we may use:\\
$AB$: At bats\\ 
$AVG$: Batting average\\ 
$H$: Hits\\
$K$: Killed,Strikeout \\
$HR$: Home Run\\
$BABIP$: Batting Average on Balls in Play\\
$SF$: sacrifice flies\\
\begin{equation}
  \label{eq:AVG}
  AVG = H/AB,
\end{equation}
which means the total number of hits divided by the total number of at-bats
\begin{equation}
  \label{eq:BABIP}
  BABIP = (H - HR) / (AB - K - HR - SF),
\end{equation}
which states that a batter's average for balls that are put in play (excludes strikeouts, home runs, and sacrifice flies)

We can see the number of players in each team in Figure~\ref{fig:team}.
\graphicspath{{images/}}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{baseball team.pdf}
  \caption{The number of players in each team in 2016 batting dataset}
  \label{fig:team}
\end{figure}

\section{Methods}
\label{sec:meth}
We will use UConn baseball team data for our research and use Wyers's method \citet*{web:Wyers:Part2} that "
A player's value is essentially an average team's runs or wins with that player, minus their runs or wins without 
that player."

\section{Results}
\label{sec:resu}
These limitations encompassed various factors, including but not restricted to the sample size, the participants' in-season playing time,
and the number of at-bats and innings pitched. The relatively small sample size utilized in the study, which significantly impacted the practicality of the results Table~\ref{tab:rv}.

\begin{table}[tbp]
  \caption{The distribution of censored participants}
  \label{tab:rv}
\centering
\begin{tabular}{rrrr}
  \toprule
  Position & Assigned Group & Did Not Meet AB or IP & Did Not Play\\ 
  \midrule
Pitcher & Control & 3 & 1\\
Pitcher & Experiment & 2 & 1\\
Infield & Control & 1 & 0 \\
Infield & Experiment & 2 & 2\\
Outfield & Control & 1 & 0\\
Outfield & Experiment & 1 & 0\\
  \bottomrule
\end{tabular}
\end{table}

The study involved recruiting 26 members from the baseball team. Among these participants, 0.385, were pitchers, 0.423 were infielders, and 0.192 were outfielders. 
Splitting these groups, half of the pitchers were in the control group, while the remaining half were in the experimental group. For the infielders, 
0.455 were in the control group, and 0.545 were in the experimental group. As for the outfielders, 0.4 were in the control group, and 0.6 were in the experimental group.
Due to limitations in the sample size—considered small—the study's reliability may have been affected since it was conducted as a convenience sample. 
While the recruitment method was straightforward as it targeted the university's varsity team, the size of the sample could potentially impact the study's outcomes. 
Notably, the study would have ideally required a minimum sample size of 128, calculated using a specific formula considering an alpha level of .05, t-tests for independent groups, 
an effect size of 0.5, and a power of 0.8. Implementing this study on a larger scale, such as within a Minor League Baseball organization, 
would have made achieving the required sample size more feasible.

>>>>

\documentclass[12pt]{article}
\usepackage{setspace}
\doublespacing

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

Every value indicator has an underlying baseline, whether by chance or design. As a result, it is advisable to 
carefully analyze the choice of a baseline and the reasoning behind it. Baselines are important since we are not 
interested in a single player - there is no such thing as a baseball player in isolation. We're interested in a 
player's contributions in the context of a team - the marginal contribution of that player in comparison to who 
else could have played instead. If you've ever spent a lot of time on baseball forums or message boards, you've 
probably seen an idea that starts with, "What could it hurt to do this?" It's the opportunity cost: playing time 
is a fixed commodity that cannot be transferred from one player to another. Now let's start to talk about the
detail process of value baseball players.

@@

A discussion concludes in Section~\ref{sec:disc}.

\section{Data}
\label{sec:data}

We got the 2008 season stats for 30 teams from Fangraphs website, including team name, plate appearence, average, 
pitches and so on. We then process the data we collect using the code mentioned in Figure~ \ref*{fig:baseballcode}.The 
data \ref{tab:PF_PFPA} and all player data is drawn from the Stats section of Fangraphs \cite*{web:data}.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{baseballcode.pdf}
  \caption{code for addressing stats 2008 baseball team}
  \label{fig:baseballcode}
\end{figure}

\section{Methods}
\label{sec:meth}

As Wyers mentioned  "A player's value is essentially an average team's 
runs or wins with that player, minus their runs or wins without that player." \citep*{web:Wyers:Part2} We have two 
types of models: dynamic and linear. Dynamic models excel in assessing entire contexts, such as a team's overall performance or 
a pitcher's effectiveness. However, they are less effective when applied to individual hitters, as each hitter 
only influences a fraction of the overall context. Additionally, a hitter's performance 
does not interact with itself; for instance, if a hitter walks, they cannot subsequently hit a home run to drive 
themselves in.

On the other hand, linear models are adept at capturing the environmental context, making them 
well-suited for estimating a hitter's contribution to a specific context. However, they may not perform as 
effectively when evaluating pitchers.

Among dynamic run estimators, BaseRuns stands out as the most accurate and versatile. The formula for BaseRuns is:

\begin{equation}
  \label{eq:baseRuns}
A*B/(B + C) + D
\end{equation}

Where $A$ is the number of baserunners, $B$ is the “advancement factor,” $C$ is the number of outs, and $D$ is the 
number of home runs.

There are nearly too many linear weights formulas to name when it comes to linear run estimators. It's generally 
ideal to utilize bespoke linear weights dependent on the season for a player value system. The most important 
factor to consider is baseline—while all dynamic run estimators provide absolute runs, certain linear run estimators
provide runs above average instead.

Following are definitions we may use:
\begin{table}[htbp]
  \caption{Baseball Batting Statistics}
  \label{tab:discription} 
  \centering
  \begin{tabular}{|l|l|}
     \hline
     \textbf{Variable} & \textbf{Description}\\
     \hline
     $AB$ & At bats\\
     $AVG$ & Batting average\\
     $H$ & Hits\\
     $K$ & Strikeouts\\
     $HR$ & Home Run\\
     $BABIP$ & Batting Average on Balls in Play\\
     $SF$ & Sacrifice flies\\
    \hline
  \end{tabular}
\end{table}

\begin{equation}
  \label{eq:AVG}
  AVG = H/AB,
\end{equation}
which means the total number of hits divided by the total number of at-bats
\begin{equation}
  \label{eq:BABIP}
  BABIP = (H - HR) / (AB - K - HR - SF),
\end{equation}
which states that a batter's average for balls that are put in play (excludes strikeouts, home runs, and 
sacrifice flies)

\section{Results}
\label{sec:resu}
In assessing a player's offensive value, a linear system proves to be most effective. Linear systems
provide insights into the number of runs a player adds to an average team. It's important 
to note that linear weights values may not necessarily sum up to team totals accurately, 
particularly for teams that excel or struggle significantly on the offensive front. If we're going to use a 
linear run estimator, shouldn't we also use a linear park factor? We simply 
take the average number of runs per plate appearance—roughly.122 in 2008—and park compensate for the 
difference. Simply multiply that figure by the number of plate appearances and add it to the 
linear weight values to get your park adjustment. And that is all there is to it. Simply put, 
you have a measure of a player's offensive worth relative to the average.
This gives us a linear factor to work with, as shown Table~ \ref*{tab:PF_PFPA}

\begin{table}[ht]
  \caption{Park value formula and its per plate appearance in each team}
  \label{tab:PF_PFPA} 
  \centering
  \resizebox{\columnwidth}{!}{
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
      \hline
      TEAM & PF & PFPA & TEAM & PF & PFPA & TEAM & PF & PFPA\\ 
      \hline
     ARI & 1.05 & 0.006 & ATL & 1.00 & 0.000 & BAL & 1.01 & 0.001\\
     BOS & 1.04 & 0.005 & CHA & 1.04 & 0.005 & CHN & 1.04 & 0.005\\
     CIN & 1.02 & 0.002 & CLE & 1.00 & 0.000 & COL & 1.09 & 0.011\\
     DET & 1.00 & 0.000 & FLA & 0.98 & -0.002 & HOU & 0.99 & -0.001\\
     KC & 1.00 & 0.000 & LAA & 0.98 & -0.002 & LAN & 0.99 & -0.001\\
     MIL & 1.00 & 0.000 & MIN & 1.00 & 0.000 & NYA & 1.00 & 0.000\\
     NYN & 0.97 & -0.004 & OAK & 0.98 & -0.002 & PHI & 1.02 & 0.002\\
     PIT & 0.98 & -0.002 & SD & 0.92 & -0.010 &SEA & 0.97 & -0.004 \\
     SF & 1.01 & 0.001 & STL & 0.98 & -0.002 &TB & 0.99 & -0.001\\
     TEX & 1.03 & 0.004 & TOR & 1.02 & 0.002 & WAS & 1.01 & 0.001\\

    \end{tabular}
  }
  \cite*{web:Wyers:Part3}
\end{table}

Now we should consider defense value of a player. Begin using the Revised Zone Rating statistics \citep*{web:Studeman2007Field} 
available on THT (Figure~\ref*{fig:baseballcode}). We have a metric for playing time 
(BIZ, or balls in zone) and plays made (Plays and OOZ, or out of zone plays). What we want to 
do is compare these to the average, convert the plays to runs, and then correct for position differences.
\begin{equation}
  \label{eq:RZR}
  BIZ * (PlayerRZR - LeagueRZR) + Innings * (PlayerOOZ/PlayerInn - LeagueOOZ/LeagueInn)
\end{equation}

Subsequently, converting plays to runs involves a straightforward application of a constant. The adjustment
for position is then made by distributing the variance between positions proportionally according to playing 
time. This positional adjustment should be determined by assessing the relative defensive difficulty among 
positions, a measurement attainable by examining players who occupy multiple positions. Table~\ref*{tab:def_metrics}
is the comprehensive breakdown.

\begin{table}[htp]
  \caption{Full Nitty-Gritty}
  \label{tab:def_metrics} 
  \centering
  \resizebox{\columnwidth}{!}{
    \begin{tabular}{|l|c|c|c|c|c|c|}
     \hline
      Position & RZR (Revised Zone Rating) & OOZ\_INN (Out of Zone Plays per Inning) & Run/Play & BIZ/30 (Balls in Zone per 30 Innings) & PAdj (Positional Adjustment)\\
     \hline
     1B & 0.739422 & 0.030305 & 0.798 & 219 & -12.5\\
     2B & 0.821831 & 0.026007 & 0.754 & 426 & 2.5\\
     3B & 0.696536 & 0.038408 & 0.8 & 354.1333 & 2.5\\
     CF & 0.921688 & 0.067393 & 0.842 & 349.0333 & 2.5\\
     LF & 0.882837 & 0.04453 & 0.831 & 275.4 & -7.5\\
     RF & 0.899098 & 0.048531 & 0.843 & 292.0333 & -7.5\\
     SS & 0.828403 & 0.037678 & 0.753 & 424.8333 & 7.5\\
    \end{tabular}
  }
\cite*{web:Wyers:Part3}
\end{table}

The top 10 position players, 2008

\begin{table}[htbp]
  \caption{Top 10 Player in 2008}
  \label{tab:top} 
  \centering
  \begin{tabular}{|l|l|c|c|c|c|c|}
     \hline
     \textbf{Last Name} & \textbf{First Name} & \textbf{Offesne} & \textbf{Bonus} & \textbf{Defense} & \textbf{Total} & \textbf{WAR}\\
     \hline
     Pujols & Albert & 73.3 & 18.3 & 16.7 & 108.4 & 10.8\\
     Jones & Chipper & 51.5 & 15.3 & 18.1 & 84.9 & 8.5\\
     Utley & Chase & 33.6 & 20.2 & 30.0 & 83.7 & 8.4\\
     Berkman & Lance & 49.5 & 19.0 & 12.6 & 81.0 & 8.1\\
     Rodriguez & Alex & 39.0 & 21.2 & 14.3 & 74.4 & 7.4\\
     Teixeira & Mark & 45.5 & 21.2 & 7.2 & 74.0 & 7.4\\
     Ramirez & Hanley & 40.8 & 19.8 & 9.6 & 70.2 & 7.0\\
     Wright & David A & 41.0 & 21.0 & 7.3 & 69.4 & 6.9\\
     Beltran & Carlos & 30.4 & 20.2 & 16.8 & 67.4 & 6.7\\
     Sizemore & Grady & 30.1 & 26.6 & 8.1 & 64.8 & 6.5\\
    \hline
  \end{tabular}
\end{table}

The buttom 10 position players, 2008
\begin{table}[htbp]
  \caption{Buttom 10 Players in 2008}
  \label{tab:buttom} 
  \centering
  \begin{tabular}{|l|l|c|c|c|c|c|}
     \hline
     \textbf{Last Name} & \textbf{First Name} & \textbf{Offense} & \textbf{RepBonus} & \textbf{Defense} & \textbf{Total} & \textbf{WAR}\\
     \hline
     Wilkerson & Brad & -13.9 & 11.0 & -9.4 & -12.3 & -1.2\\
     Balentien & Wladimir R & -16.1 & 9.3 & -6.0 & -12.9 & -1.3\\
     Jacobs & Mike & 5.4 & 14.8 & -31.5 & -11.3 & -1.1\\
     Matthews Jr. & Gary & -12.6 & 17.0 & -16.4 & -11.9 & -1.2\\
     Patterson & Corey & -29.4 & 11.2 & 4.7 & -13.5 & -1.4\\
     Lamb & Mike & -15.6 & 9.6 & -8.5 & -14.4 & -1.4\\
     Francoeur & Jeff B & -26.0 & 18.7 & -4.6 & -11.9 & -1.2\\
     Pena & Tony F & -30.4 & 8.4 & 6.2 & -15.8 & -1.6\\
     Guillen & Jose & -9.7 & 22.6 & -28.3 & -15.4 & -1.5\\
     Gload & Ross & -15.4 & 14.9 & -20.1 & -20.6 & -2.1\\
    \hline
  \end{tabular}
\end{table}

\section{discussion}
\label{sec:disc}

These models are not flawless since no model is. We should constantly 
strive to improve these models.At THT, we use Fielding Independent Pitching, a basic but successful 
methodology. However,to apply linear models to pitching and thus 
employ a dynamic FIP based on BaseRuns. In most circumstances, the distinction is likely to be trivial, 
but for exceptionally good or awful pitchers, it will be significant.

Besides, some Baseball fans can be tremendously protective of their home team's players 
- or they can be incredibly vicious. This is heavily influenced by how good this player 
is and how well the team has lately performed. Fans also like to believe that their long, 
patient commitment to their ballclub has resulted in an unfathomable amount of knowledge about 
the players they follow that is not readily available to outsiders.

Analyzing player performance in baseball necessitates a holistic approach that extends beyond 
the confines of a single season or a limited set of matches. While the data from Fangraphs in 2008 provides 
valuable insights, it is crucial to recognize that a player's true quality is multifaceted. Factors such as mental
acuity, strategic prowess, and long-term growth rates play pivotal roles in shaping a player's overall 
competence in baseball.

In order to comprehensively evaluate and understand a player's capabilities, it becomes imperative 
to gather a more extensive dataset spanning multiple seasons. This broader scope allows for a nuanced 
examination of a player's consistency, adaptability, and resilience over time. Moreover, developing more 
sophisticated and comprehensive analytical models can enhance our ability to unravel the intricate layers of 
a player's performance, going beyond mere statistical outputs to capture the intangible qualities that contribute
to their success on the baseball field. By incorporating a diverse range of factors, we can build models 
that provide a more accurate and nuanced representation of a player's true value within the sport.
